Discrimination in police award nomination in Chicago

### 2024-02-14 outputs/paper/paper.qmd
Updated simulation / Added final lm table.

kable(baseline_characteristics)
as_flextable(baseline_characteristics)
```

@@

```{r}
#| echo: false
org_model <- lm(awd_perf ~ Black + Female + Hisp + Asian + Natam, data = all_officer_year)
org_model
```

Model 1
```{=tex}
\begin{align}
y &= \beta_0 + \beta_1 Black_i + \beta_2 Female_i + \beta_3 Hispanic_i \\
&+ \beta_4 Asian_i + \epsilon
\end{align}
```

```{r}
#| echo: false
modified_model <- lm(awd_perf ~ Black + Female + Hisp + Asian, data = all_officer_year)
as_flextable(modified_model)
```
```{r}
#| echo: false
black_female <- lm(awd_perf ~ Black + Female + Black:Female, 
                   data = all_officer_year)
as_flextable(black_female)
```
From this, we form a regression model to estimate the disparity gaps in award nomination between majority (white and/or male) and minority (black and/or female). The following model is the regression: y = beta0 + beta1*black + beta2*female + beta3*Hispanic + beta4*Asian where y is the number of award nomination received by an officer in one year.

>>>>

kable(baseline_characteristics)
```

@@

```{r}
#| echo: false
org_model <- lm(awd_perf ~ Black + Female + Hisp + Asian + Natam, data = all_officer_year)
as_flextable(org_model)
```

```{r}
#| echo: false
black_female <- lm(awd_perf ~ Black + Female + Black:Female, 
                   data = all_officer_year)
as_flextable(black_female)
```
From this, we form a regression model to estimate the disparity gaps in award nomination between majority (white and/or male) and minority (black and/or female). The following model is the regression: y = beta0 + beta1*black + beta2*female + beta3*Hispanic + beta4*Asian where y is the number of award nomination received by an officer in one year.

Based on previous linear model we could derive

```{r}
#| echo: false
bl_fm <- c("Black", "Female", "Black x Female", "Mean")
first <- c(-10.368, -12.826, "", 35.307)
second <- c(-10.180, -14.879, 8.315, "")
final_model <- data.frame(bl_fm, first, second)
kable(final_model, col.names = c("", "(1)", "(2)"))
```
